### 2021-09-29 docs/paper/sections/7_evaluation.tex
Try to fix paper template on CI

@@

>>>>

Rename into discussion?

@@

research questions:

-(RQ0) (how useful are these data?)
-(RQ1) what is the quality of collected dependencies?
-(RQ2) what is the quality of mined usage samples?
-(RQ3) how well is the tool applicable?

\# actual evaluation

\#\# rq1

- numbers of dependencies found for example packages (table for small, medium, large packages) for all approaches

<choose subset from excel>

NEXT: beispiele für fehler sammeln. slides damit ergänzen, fazit ziehen.

- resources: fetch metadata/download speed (zusammen 25 Pakete/min); disk space per dependency (ca. 703 KB/package); API restrictions (free, no limitations known)
- correctness: superfluous dependency specifications (TODO: count false positives by comparing with references, manually check)
limitations:
- false positives:
	* type defs
- missing dependencies: repositories without proper package manifest file
- ranking: small repositories will be underrepresented

\#\# rq2

- numbers of dependencies and references found for example packages (table for small, medium, large packages)
- resources: speed per package (20 pkgs/min), RAM/ROM
- precision/correctness: proof that there are no false positives (given correctness of tsc)
- false negatives/recall - (real) examples:
	* limited matches due to lack of type information for other frameworks used (but we could solve this); extreme metaprogramming (eval, Function.call(), .../limitations of typescript)
	* additional build steps (code generation, transpilers, ...)

\#\# rq3

- expert interviews?
- experience report (short case study looking at a certain package)
- comparison to hora2015apiwave or de2013multi? (or does this rather belong to relwork?)

\# discussion

### 2021-09-29 docs/paper/sections/8_conclusion.tex
Try to fix paper template on CI

\section{Conclusion}
\label{sec:conclusion}

@@

>>>>

\section{Conclusion and future work}
\label{sec:conclusion}

@@

future work:

* evaluation as future work:

	- rq2 - false negatives durch annotation ermitteln
	- rq3 - user study

* pattern analysis -> sample classification, potential for reuse
* dynamic analysis -> parameter/return value insights, coverage detection
* dependency classification/clustering through metrics (number of references, coupling)

minor:
* support more AST pattern (e.g. import())

STEHENGEBLIEBEN: Notizen hierfür, in slides übernehmen, dann weitere Notizen für Präsi anwenden. Heute nochmal durchsprehcne?
